Adaptive Exponentiated Gradient

### 2014-01-25 lp/summary-of-results.tex
initial paper

Let $\Var_i \eqdef \sum_{t=1}^T (z_{t,i}-\mu_i)^2$, with $\mu \eqdef \frac{1}{T} \sum_{t=1}^T z_t$.
\begin{corollary}
In the above setting, for the choice $s_t = \frac{1}{t} \sum_{s=1}^{t-1} z_s$, the 
regret relative to $w$ is bounded by
\[ \frac{\log(n)}{\eta} + \eta \sum_{i=1}^n w_i\Var_i + O(\log(T)). \]
\end{corollary}

These same results hold in the matrix case. Now we assume that $-I \preceq Z_t \preceq I$ 
and continue to assume that $\eta \leq \frac{1}{2}$:
\begin{theorem}
For a sequence $S_1, \ldots, S_T$ of symmetric matrices, consider the following 
prediction algorithm:
\begin{enumerate}
\item Predict $W_t \propto \exp(X_t - \eta S_t)$.
\item Receive loss $\Tr(W_t^{\top}Z_t)$.
\item Update $X_{t+1} = X_t - \eta Z_t - \eta^2 (Z_t-S_t)^2$.
\end{enumerate}
Then the regret relative to a fixed matrix $W$ is bounded by
\[ \frac{\log(n)}{\eta} + \eta \sum_{i=1}^n \Tr((Z_t-S_t)^{\top}W(Z_t-S_t)). \]
\end{theorem}
We now define $\Var$ to be the matrix $\sum_{t=1}^T (Z_t-M)^2$, with $M \eqdef \frac{1}{T} \sum_{t=1}^T Z_t$.
\begin{corollary}
In the matrix setting, for the cohice $S_t = \frac{1}{t} \sum_{s=1}^{t-1} Z_s$, the 
regret relative to $w$ is bounded by
\[ \frac{\log(n)}{\eta} + \eta \Tr(W^{\top}\Var) + O(\log(T)). \]
\end{corollary}
It is important to note that in all of these bounds, the $O(\log(T))$ term does not 
contain any hidden factors of $n$ or $\eta$. In fact we could take $O(\log(T)) = 8\log(T) + 2$.

>>>>

Let $\Var_i \eqdef \sum_{t=1}^T (z_{t,i}-\mu_i)^2$, with $\mu \eqdef \frac{1}{T} \sum_{t=1}^T z_t$.
\begin{corollary}
In the above setting, for the choice $s_t = \frac{1}{t} \sum_{s=1}^{t-1} z_s$, the 
regret relative to $w$ is bounded by
\[ \frac{\log(n)}{\eta} + \eta \sum_{i=1}^n w_i\Var_i + O(\log(T)). \]
\end{corollary}
This result is a slight strengthening of one of the main results in the Hazan-Kale paper I showed you today. 
The places where it is stronger are that the constant is much better (additive $\log(T)$ rather than 
multiplicative factor of $16$) and also the regret is just in terms of the variance of the best expert, 
whereas before it was a more complicated metric in terms of largest cumulative variance of best expert 
at any point in time.

These same results hold in the matrix case. Now we assume that $-I \preceq Z_t \preceq I$ 
and continue to assume that $\eta \leq \frac{1}{2}$:
\begin{theorem}
For a sequence $S_1, \ldots, S_T$ of symmetric matrices, consider the following 
prediction algorithm:
\begin{enumerate}
\item Predict $W_t \propto \exp(X_t - \eta S_t)$.
\item Receive loss $\Tr(W_t^{\top}Z_t)$.
\item Update $X_{t+1} = X_t - \eta Z_t - \eta^2 (Z_t-S_t)^2$.
\end{enumerate}
Then the regret relative to a fixed matrix $W$ is bounded by
\[ \frac{\log(n)}{\eta} + \eta \sum_{i=1}^n \Tr((Z_t-S_t)^{\top}W(Z_t-S_t)). \]
\end{theorem}
We now define $\Var$ to be the matrix $\sum_{t=1}^T (Z_t-M)^2$, with $M \eqdef \frac{1}{T} \sum_{t=1}^T Z_t$.
\begin{corollary}
In the matrix setting, for the cohice $S_t = \frac{1}{t} \sum_{s=1}^{t-1} Z_s$, the 
regret relative to $w$ is bounded by
\[ \frac{\log(n)}{\eta} + \eta \Tr(W^{\top}\Var) + O(\log(T)). \]
\end{corollary}
It is important to note that in all of these bounds, the $O(\log(T))$ term does not 
contain any hidden factors of $n$ or $\eta$. In fact we could take $O(\log(T)) = 8\log(T) + 2$.
As far as I'm aware, both the theorem and the corollary in the matrix case are new. But 
a lot of the work done on this is in the theory community and I haven't reviewed 
references on matrix multiplicative weights nearly as thoroughly as for online learning.
